### 2022-11-22 paper-thesis/chapters/20-adding-booleans.tex
A section about inference

\chapter{\label{chap:bools}Booleans and other "simple" constructs that really need a better title}

@@

	\inferrule{
		\bhr
		{ \scope{s}{c} }
		{ [] }
		{ \scope{s'}{BoolTrue()} }
		\\\bhr
		{ \scope{s}{b1} }
		{ t }
		{ \scope{s''}{b1'} }
	} {
		\bhr
		{ \scope{s}{\co{BoolIf}(c, b1, b2)} }
		{ t }
		{ \scope{s}{b1'}}
	}

	\inferrule{
		\bhr
		{ \scope{s}{c} }
		{ [] }
		{ \scope{s'}{BoolFalse()} }
		\\\bhr
		{ \scope{s}{b2} }
		{ t }
		{ \scope{s''}{b2'} }
	} {
		\bhr
		{ \scope{s}{\co{BoolIf}(c, b1, b2)} }
		{ t }
		{ \scope{s}{b2'}}
	}
\end{mathpar}
\caption{Rules for beta head reducing booleans}
\label{fig:bool-rules-beta}
\end{figure}

@@

\begin{figure}[ht]
\begin{mathpar}
	\inferrule{
	} {
		\toe{s}{BoolType()}{Type()}
	}

	\inferrule{
	} {
		\toe{s}{BoolTrue()}{BoolType()}
	}

	\inferrule{
	} {
		\toe{s}{BoolFalse()}{BoolType()}
	}

	\inferrule{
		\toe{s}{c}{ct}
		\\\beq{ct}{BoolType()}
		\\\\
		\\\toe{s}{b1}{tb1}
		\\\toe{s}{b2}{tb2}
		\\\beq{tb1}{tb2}
	} {
		\toe{s}{BoolIf(c, b1, b2)}{tb1}
	}
\end{mathpar}
\caption{Rules for type checking booleans}
\label{fig:bool-rules-typecheck}
\end{figure}

@@

Next we will add \verb|Postulate| to the language.

@@

>>>>

\chapter{\label{chap:bools}Extending the language}

@@

	\inferrule{
		\bhr
		{ \scope{s}{c} }
		{ [] }
		{ \scope{s'}{\co{BoolTrue}()} }
		\\\bhr
		{ \scope{s}{b1} }
		{ t }
		{ \scope{s''}{b1'} }
	} {
		\bhr
		{ \scope{s}{\co{BoolIf}(c, b1, b2)} }
		{ t }
		{ \scope{s}{b1'}}
	}

	\inferrule{
		\bhr
		{ \scope{s}{c} }
		{ [] }
		{ \scope{s'}{\co{BoolFalse}()} }
		\\\bhr
		{ \scope{s}{b2} }
		{ t }
		{ \scope{s''}{b2'} }
	} {
		\bhr
		{ \scope{s}{\co{BoolIf}(c, b1, b2)} }
		{ t }
		{ \scope{s}{b2'}}
	}
\end{mathpar}
\caption{Rules for beta head reducing booleans}
\label{fig:bool-rules-beta}
\end{figure}

@@

\begin{figure}[ht]
\begin{mathpar}
	\inferrule{
	} {
		\toe{s}{\co{BoolType}()}{\co{Type}()}
	}

	\inferrule{
	} {
		\toe{s}{\co{BoolTrue}()}{\co{BoolType}()}
	}

	\inferrule{
	} {
		\toe{s}{\co{BoolFalse}()}{\co{BoolType}()}
	}

	\inferrule{
		\toe{s}{c}{ct}
		\\\beq{ct}{\co{BoolType}()}
		\\\\
		\\\toe{s}{b1}{tb1}
		\\\toe{s}{b2}{tb2}
		\\\beq{tb1}{tb2}
	} {
		\toe{s}{\co{BoolIf}(c, b1, b2)}{tb1}
	}
\end{mathpar}
\caption{Rules for type checking booleans}
\label{fig:bool-rules-typecheck}
\end{figure}

@@

Next we will add \verb|Postulate| to the language. A postulate declares that there is a variable with a certain type, without specifying a value. Through the view of the Curry-Howard correspondence, this is equivalent to an axiom. At the current stage, this is useful for testing the language. For example, this is a test with a postulate:

\begin{lstlisting}
postulate T : Type;
if true then Bool else T end
\end{lstlisting}
The following rules are used to implement the feature, which translate cleanly to Statix:

\begin{figure}[ht]
	\begin{mathpar}
		\inferrule{
			\bhr
			{\scope{s}{b}}
			{a}
			{\scope{s'}{b'}}
		}{
			\bhr
			{\scope{s}{\co{Postulate}(n, t, b)}}
			{a}
			{\scope{s'}{b'}}
		}

		\inferrule{
			\toe{s}{t}{tt}
			\\\beq{tt}{\co{Type}()}
			\\\\\bred{s}{t}{t'}
			\\\toe{\co{sPutType}(s, n, t')}{b}{bt}
		} {
			\toe{s}{\co{Postulate}(n, t, b)}{bt}
		}
	\end{mathpar}
	\caption{Rules for postulates}
	\label{fig:postulate-rules}
\end{figure}

@@

\section{Extensibility of the approach}
